---
title: "Getting started with R and RStudio"
author: "Oscar Rodriguez de Rivera"
date: "24-04-2023"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Within this module we are going to be introducing you to a computing language called R. You will also be making use of R within later modules during your degree course. We use an interface to R called RStudio which provides a more user-friendly setting in which to code. This worksheet will introduce you to some basic aspects of using R and RStudio. Work through each of the tasks below and answer the questions set.

### Navigating RStudio

### R Scripts and Loading Data into R

When you have a small amount of data you can type data directly into R. The c( ) function in R is used to create a vector with values you provide explicitly. Suppose we wish to define a variable *X* to be a vector of numbers 1, 5, 6 and 10. To load this vector into R we would type:

```{r}
X <- c(1, 5, 6, 10)
```

Try typing the code above into the console window of RStudio (left hand window). These 4 values are then stored in an object named X and you can call them by typing:

    X

The command \< − means "is assigned", Y\<-10 is equivalent of saying variable Y takes the value 10. To call one of the elements of X we can do this using square brackets, [ ]. For example, try typing `X[2]`

```{r}
X[2]
```

in the console window, which calls the 2nd element of X, which is the value 5. You should see the following output: `[1] 5`

[Exercise]{.underline}

Download the R Script TestScript.R from moodle and save it in your working directory. It will appear as a text file. In RStudio, to convert it to an R Script, select the following tabs (top left): File $\rightarrow$ New File $\rightarrow$ RScript Copy and paste the commands into this file and save the file to your working directory using 'Save as'. Practice running the script. What does this R code do?

The script file TestScript.R contains the following commands.

```{r}
Y1<-1:10 # The : command defines the integer values from 1 up to 10
Y1
```

```{r}
Y2<-11:20  # Here we define the integer values from 11 up to 20
Y2
```

```{r}
Y<-c(Y1,Y2)  # Y combines vectors Y1 and Y2 and we now have a new vector called
Y              # Y which contains the integer values from 1 up to 20.
```

```{r}
Z<-Y[-2]  # Z is defined to be the vector Y but with the 2nd element removed
Z
```

```{r}
Z[c(3,6,9)]  # Here we have called the 3rd, 6th and 9th element of vector Z
```

There are some sample data sets on moodle: birdexample.xls, Temperature.xls and parkrun.txt. Download these files from moodle into the folder you have set as your working directory.

-   Load parkrun.txt into R. The data set is now stored in an object called parkrun.
-   parkrun contains 3 variables: `Run_Number, Male and Female`

Suppose we wish to define a vector, which we shall call PRmale, of the variable Male. We can do this by using the command:

`PRmale<-parkrun$Male`

-   Alternatively suppose we wish to be able to just call the variables directly without defining new variables, we can do this by attaching parkrun to our environment using the command

`attach(parkrun)`

Now you can simply call:

`Male`

-   Try loading the other two data sets, birdexample.xls and Temperature.xlsx into R and check that the variables have got appropriate names and that they have appeared in your R environment. Test calling the variables using the \$ option and using the attach command.

### Exercises

Write your answers to these exercises in an R Script file so that you can save it and re-run your code when you wish. If you wish to annotate your code with comments about what certain commands do you can use the \# command in your R Script file - anything on the line which appears after the \# will be ignored by R when the script is run.

1.  Within this exercise you are going to learn about the function rep. Note to get more information about inbuilt R functions you can type the command

`?rep`

which will open the help file about function rep.

a.  Use the function `c()` to define the vector *x* = (12, 3, 2, 6).
b.  Enter the following function, what does it do?

`rep(x,2)`

c.  Enter the following function, what does it do?

    `rep(x,c(2,2,2,2))`

d.  What command would we use to get the following output?

    `[1] 12 3 3 2 2 6 6 6`

```{=html}
<!-- -->
```
2.  Recall that a vector is an ordered set of values and the simplest way to define a vector is by the c() command. Define the vectors x and y:

    `x<-c(1,2,3)`

    `y<-c(0,1,2,3)`

```{=html}
<!-- -->
```
a.  Add 1 to each element of x by typing:

    `x+1`

b.  How would we obtain the following output?

    `[1] 2 3 4 5`

```{=html}
<!-- -->
```
3.  Input the vector *v* = (3, 6, 9, 6). What do the following commands do?

```{=html}
<!-- -->
```
a.  1/v
b.  max(v)
c.  min(v)
d.  sum(v)
e.  prod(v)
f.  sort(v)
g.  order(v)
