---
title: "Choosing and renaming columns and rows"
author: "Oscar Rodriguez de Rivera"
date: "2023-04-25"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Choosing columns by name

#### Manual naming

You can choose columns using dplyr::select(). The most basic method of choosing columns is to name them:

```{r}
library(tidyverse)
starwars %>%
dplyr::select(name, height, mass) %>%
glimpse()
```

Another method is to name a set of adjacent columns using the : operator, just as you would create a range of numbers from 1 to 4 with 1:4:

```{r}
starwars %>%
    dplyr::select(name:mass) %>%
    glimpse()
```

we can select all columns from `iris` that measure `Petal`, or all columns that measure `Length`, or any column that has a `.`:

```{r}
iris %>%
dplyr::select(starts_with("Petal")) %>%
glimpse()
```

```{r}
iris %>%
dplyr::select(ends_with("Length")) %>%
glimpse()
```

```{r}
iris %>%
dplyr::select(contains(".")) %>%
glimpse()
```

#### Reordering columns

```{r}
iris %>%
dplyr::select(ends_with("Length"), Species, ends_with("Width")) %>%
glimpse()
```

The `everything()` selector returns every column that isn’t already selected, which makes it useful for reordering a data frame’s columns:

```{r}
iris %>%
    dplyr::select(Species, everything()) %>% # Reorder 'Species' to the first column
    glimpse()
```

#### Omitting columns

With any of the above methods, you can omit a column by putting a - in front of the selection:

```{r}
iris %>%
    # Negate the selector to omit its results
    #         ↓
dplyr::select(-Species, -Petal.Length) %>%
glimpse()
```

```{r}
iris %>%
dplyr::select(-ends_with("Length")) %>%
glimpse()
```

### Choosing columns by value

You can choose columns based on whether they satisfy a logical test by using the special verb `select_if()`. For example, we can choose columns by data type:

```{r}
starwars %>%
select_if(is.numeric) %>% # Using the base R function is.numeric()
glimpse()
```

Or we can choose columns that meet some arbitrary check by writing our own function that returns TRUE or FALSE:

```{r}
colSums(iris[1:4])
```

```{r}
less_than_500 <- function(x) {
sum(x) < 500
}

iris[1:4] %>%
select_if(less_than_500) %>%
glimpse()
```

We can use the tilde ($\sim$) as a shortcut to write an anonymous function, so the above could be expressed like this:

```{r}
iris[1:4] %>%
select_if(~ sum(.) < 500) %>%
glimpse()
```

### Renaming columns

```{r}
library(janitor)
# Standardise names with janitor::clean_names()
iris %>%
clean_names() %>%
names() # Print the column names
```

```{r}
# Replace all names with purrr::set_names()
iris %>%
set_names("sep_len", "sep_wid", "pet_len", "pet_wid", "spp") %>%
names()
```

```{r}
# Replace some names with dplyr::rename()
iris %>%
rename(sep_length = Sepal.Length, sep_width = Sepal.Width) %>%
names()
```

### Building a dataset with duplicated rows

To illustrate subsetting, we will make a special version of the built-in starwars dataset that contains some duplicated rows:

```{r}
set.seed(896)
sw_dup <-
starwars %>%
dplyr::select(-(films:starships)) %>% # Omit the last 3 columns (they are lists)
sample_n(100, replace = TRUE) %>% # replace = TRUE to get duplicate rows.
glimpse()
```

### Reordering rows

```{r}
sw_dup <-
sw_dup %>%
# Sort rows by homeworld, then species, then name.
arrange(homeworld, species, name) %>%
glimpse()
```

The default sorting order of arrange() is A-Z for Character columns and in increasing order for Numeric and Factor columns. To sort in the opposite direction, use desc():

```{r}
sw_dup %>%
arrange(mass) %>% # Increasing quantity of mass
glimpse()
```

```{r}
sw_dup %>%
arrange(desc(mass)) %>% # Decreasing mass
glimpse()
```

### Removing duplicate rows

Use dplyr::distinct() to remove duplicate rows. By default, it will remove a row if every one of its values is identical to a previous row’s values (i.e. it keeps the first instance of a duplicated row and discards the other copies).

```{r}
sw_dup %>%
distinct() %>%
glimpse() %>%
anyDuplicated() # Returns 0 if there are no duplicate rows.
```

You can also choose the columns that are compared for duplication. By default it only returns the columns that were chosen; to return all of the columns, use the argument .keep_all = TRUE.

```{r}
sw_dup %>%
distinct(species, homeworld) %>% # Only check 'species' and 'homeworld'
glimpse() %>%
anyDuplicated()
```

```{r}
sw_dup %>%
distinct(species, homeworld, .keep_all = TRUE) %>% # Keep all columns
glimpse() %>%
anyDuplicated()
```

### Removing rows with NAs

Use `tidyr::drop_na()` to remove any row that contains an `NA`.

```{r}
sw_dup %>%
drop_na() %>%
glimpse() %>%
anyNA() # Returns FALSE if there are no NAs in the data frame
```

Instead of looking for NAs inside every column, you can choose only some columns. NAs that occur outside the chosen columns will be ignored.

```{r}
sw_dup %>%
drop_na(gender:species) %>%
glimpse() %>%
anyNA() # Returns TRUE because there are still NAs, e.g. in birth_year.
```

### Choosing rows by value

One of the most important verbs in `dplyr` is `dplyr::filter()`, which is used to subset a data frame to return the rows that you’re interested in.

```{r}
# Find all of the Humans whose homeworld was not Earth
sw_dup %>%
filter(species == "Human", homeworld != "Earth") %>%
distinct() %>%
glimpse()
```

```{r}
# Find everyone who is either a Droid OR whose homeworld is Tatooine
sw_dup %>%
filter(species == "Droid" | homeworld == "Tatooine") %>%
distinct() %>%
glimpse()
```

```{r}
# Find every human who either has no recorded mass, or is taller than 180 cm
sw_dup %>%
filter(species == "Human", (is.na(mass) | height > 180)) %>%
distinct() %>%
glimpse()
```

```{r}
# Find everyone who is 100-170 cm tall
sw_dup %>%
filter(between(height, 100, 170)) %>%
distinct() %>%
glimpse()
```

