---
title: "Joining data frames together"
author: "Oscar Rodriguez de Rivera"
date: "2023-04-25"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This chapter covers how to join two data frames together. Although the examples that we present involve only two data frames at a time, they can be iterated with purrr to perform complex joins.

### Classic row-binding and column-binding

The most basic methods of joining data frames are to row-bind them by stacking their rows on top of each other (if their columns are identical), or column-bind them by putting their columns beside each other (if they have the same number of columns). In the Tidyverse, these are performed by dplyr::bind_rows() and dplyr::bind_rows() respectively. Their advantage over the base functions rbind() and cbind() is that you can pass many data frames to them at once:

```{r}
library(tidyverse)
bind_rows(
sample_n(iris, 10),
sample_n(iris, 10),
sample_n(iris, 10)
) %>%
glimpse() # 30 observations (i.e. rows)
```

```{r}
bind_cols(
sample_n(iris, 10),
sample_n(iris, 10),
sample_n(iris, 10)
) %>%
glimpse() # 15 variables (i.e. columns). Columns are given unique names.
```

### Joining data frames by value

There are seven different kinds of join operations provided by dplyr, which you can read more of in ?dplyr::join. Here we draw attention to the three most useful ones:

* left_join(x, y): Column-bind values from y to their matching rows in x.
* semi_join(x, y): Only keep rows from x if they also appear in y.
* anti_join(x, y): Only keep rows from x if they do not appear in y.


```{r}
sw_all <-
starwars %>%
dplyr::select(name, homeworld, species) %>% # More select() in the next chapter
glimpse()
```

Then we will create a subset of starwars for use with semi_join() and anti_join(), and keep a different set of columns:

```{r}
set.seed(1287540661) # So we draw the same rows every time
sw_subset <-
starwars %>%
dplyr::select(name, height:eye_color, species) %>%
sample_frac(0.20) %>% # Pick 20 % of the total rows.
glimpse()
```

Joining tables requires at least one column to be the same between them, but here we have two: name and species.

#### Merge with left_join()

The most-used method is left_join(), which can be used to merge data from two tables together. For example, we have extra information about 17 of our characters:

```{r}
left_join(x = sw_all, y = sw_subset) %>%
glimpse()
```

By default, join operations will automatically try to use every identically-named column in both data frames, and then raise a message to tell you so. If you manually define the by argument, you can get control over this behaviour while removing this message:

```{r}
left_join(x = sw_all, y = sw_subset, by = "name") %>%
glimpse()
```

#### Intersect with semi_join()

Use semi_join() when you only want to keep rows that occur in two data frames.

```{r}
sw_all %>%
    left_join(sw_subset, by = c("name", "species")) %>%
    semi_join(sw_subset, by = "name") %>%
    glimpse()
```

#### Difference with ‘anti_join()

Use anti_join() when you only want to find rows that don’t occur in both data frames.

```{r}
anti_join(sw_all, sw_subset, by = c("name", "species")) %>%
  glimpse()
```

