---
title: "Distributions"
author:
- O Rodriguez de Rivera Ortega, PhD\newline
- University of Exeter
date: "12/05/2023"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Distribution playground

**Goals**

• Review the most common probability distributions used in GLMs and GLMMs

• Get a feeling for how the parameters affect the distribution shapes

• Have an interactive resource to use in the future

### Continuous distributions

#### Normal

```{r eval=FALSE, include=TRUE}
library(manipulate)
x <- seq(-10, 10, length.out = 300)
manipulate({
y <- dnorm(
x = x,
mean = mean,
sd = sd)
plot(x = x, y = y, type = "l", ylim = c(0, max(y)),
main = "Normal")},
mean = slider(-10, 10, 0),
sd = slider(0.1, 10, 2))
```

#### Log normal
```{r eval=FALSE, include=TRUE}
x <- seq(0, 100, length.out = 300)
manipulate({
y <- dlnorm(
x = x,
meanlog = meanlog,
sdlog = sdlog)
plot(x = x, y = y, type = "l", xlim = c(0, 100), ylim = c(0, max(y)),
main = "Lognormal")},
meanlog = slider(0.1, 10, 3),
sdlog = slider(0.01, 2, 1))
```

#### Gamma

What happens if the Gamma shape parameter is large and the scale parameter is small?
What happens if the Gamma scale parameter is large and the shape parameter is small?
What distributions do these resemble? Why is that useful?

```{r eval=FALSE, include=TRUE}
x <- seq(0, 100, length.out = 300)
manipulate({
y <- dgamma(
x = x,
shape = shape,
scale = scale)
plot(x = x, y = y, type = "l", ylim = c(0, max(y)),
main = "Gamma")},
shape = slider(1, 10, 3),
scale = slider(0.1, 30, 2))
```

### Discrete distributions

#### Poisson

What happens to the width of the Poisson as the mean (lambda) increases?
When might you expect to observe a Poisson distribution?
```{r eval=FALSE, include=TRUE}
x <- seq(0, 100)
manipulate({
y <- dpois(x,
lambda = lambda)
plot(x = x, y = y, type = "h", xlim = c(0, 60), ylim = c(0, max(y)),
main = "Poisson")},
lambda = slider(0.1, 30, 3))
```

####Negative Binomial

```{r eval=FALSE, include=TRUE}
x <- seq(0, 100)
manipulate({
y <- dnbinom(
x = x,
size = size,
mu = mu)
plot(x = x, y = y, type = "h", ylim = c(0, max(y)),
main = "Negative binomial")},
size = slider(0.1, 10, 1),
mu = slider(0.1, 60, 4))
```

####Binomial

```{r eval=FALSE, include=TRUE}
x <- seq(0, 10)
manipulate({
y <- dbinom(x,
size = size,
prob = prob)
plot(x = x, y = y, type = "h", xlim = c(0, 10), ylim = c(0, max(y)),
main = "Binomial")},
size = slider(1, 10, initial = 1, step = 1),
prob = slider(0, 1, initial = 0.5, step = 0.1))
```
