---
title: "Writing functions in R"
author: "Oscar Rodriguez de Rivera"
date: "25-04-2023"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

An important part in R, and in all other programming languages, is to be
able to write new functions in addition to using built in functions.
Functions include a series of expressions that often need to be executed
repeatedly. The argument values we pass in a function may change every
time we use a function so that we get different outputs.

### Introduction

Suppose we want to calculate the sum:

$$
\sum_{x=1}^{4}x=1+2+3+4=10
$$ 
This is equivalent to adding up the integers 1, 2, 3 and 4. In R we can tell it to:

```{r}
sum(1:4)
```

-   [**Exercise 1.1**]{.underline}

Suppose we now wanted to calculate $\sum_{x=1}{100}x$. What R command would we use?

**Solutions**

```{r eval=FALSE, include=FALSE}
sum(1:100)
```

### The `for` loop

Now suppose we are given the vector $n$ = (10, 20, 30) and we want to
calculate:

$$
\sum_{i=1}^{3}x=n_1+n_2+n_3=60
$$

The first thing we need to do is to define the vector n. We do this with the command:

```{r}
n <- c(10, 20, 30)
```

Next, we wish to add together the elements of n, we can simply do this using the command:

```{r}
sum(n)
```

Suppose instead that we wish to create a loop to add each element of n to the previous ones in turn. We start by defining a dummy variable, `sum_n`, that initially takes the value 0:

```{r}
sum_n <- 0
```

We then create a `for` loop. A for loop is used to repeat a task for different input values.

```{r}
for (i in 1:3) sum_n<-sum_n+n[i]
```

When $i$ = 1, sum n takes the starting value of 0 and then adds on the element $n[i]$. This then becomes the new value of `sum_n`. Next when $i$ = 2, $n[2]$ is added onto sum_n, so it is now equal to $n[1]+n[2]$.

Finally when $i$ = 3, $n[3]$ is added onto sum n, so sum $n = n[1] + n[2] + n[3]$.

-   [**Exercise 2.1**]{.underline}

Suppose we want to calculate the sum of the 2nd 4th and 6th elements
$x_2$, $x_4$ and $x_6$) of a vector x = (2, 5, 1, 8, 9, 3, 4). How would
this be coded?

**Solution**

```{r eval=FALSE, include=FALSE}
x<-c(2,5,1,8,9,3,4)
sum_x <- 0
for (i in 1:3) sum_x<-sum_x+x[2*i]
sum_x
```

Suppose we wanted to calculate

$$
\sum_{x=1}^{4}x(x+1)
$$ In R we would code this as:

```{r}
y<-0
for (x in 1:4) y<-y+x*(x+1)
y
```

-   [**Exercise 2.2**]{.underline}

Write code to calculate 
$$
\sum_{x=1}^{8}x(x+2)
$$ 

**Solution**

```{r eval=FALSE, include=FALSE}
y<-0
for (x in 1:8) y<-y+x*(x+2)
y
```

### Using the `if` command

The `if` statement in R will execute a command if a condition is
satisfied. Let us install an R package called `MASS` which contains a
number of interesting data sets. Recall, to install an Rpackage we type:

```{r}
library("MASS")
```

The data set anorexia contained within this Rpackage contains weight
information on anorexia patients pre- and post-treatment.

We first need to attach the anorexia data into our environment. To do
this we use the commands:

```{r}
data(anorexia)
attach(anorexia)
```

The attach commands mean we can now call variables Postwt and Prewt
directly. If we had not done this we would need to refer to them as
`anorexia$Postwt` and `anorexia$Prewt` which can be quite cumbersome to
type.

Suppose we want to investigate whether patient 1 gained weight after
treatment. We could use the command:

```{r}
if (Postwt[1]>Prewt[1])
{print("Patient 1 gained weight after treatment") } else
{print("Patient did not gain weight after treatment")}
```

Did patient 1 gain weight after treatment?

**Repeat the above check for patient number 15. Did patient 15 gain
weight after treatment?**

### Writing functions in R

Suppose that we wanted to be able to write code to return the sum,

$$
\sum_{i=1}^{n}i
$$ 

for any value of n you input. In order to do this we need to write a
function. A function in R will have the general form (note do not type
this into R as it will just produce an error!):

```{r}
func_name <- function(argument) {
statement
}
```

So for the problem above, we can define a function called sum.n:

```{r}
sum.n <- function(n)
{
y<-0
for (i in 1:n) {y<-y+i}
print(y)
}
```

The argument of the function in this case is n, so when we call the
function we can tell it what value of the argument we are calculating
the function for.

```{r}
sum.n(5)
```

```{r}
sum.n(10)
```

-   [**Exercise 4.1**]{.underline}

Write a function called sum.square.n that calculates 
$$
\sum_{i=1}^{n}i^2
$$ 
Evaluate the function for values of n equal to 4, 6 and 1000.

**Solution**

```{r eval=FALSE, include=FALSE}
sum.square.n <- function(n)
{
  y<-0
  for (i in 1:n) {y<-y+i*i}
  print(y)
}
```

```{r eval=FALSE, include=FALSE}
sum.square.n(4)
sum.square.n(6)
sum.square.n(1000)
```

-   [**Exercise 4.2**]{.underline}

What does the following function do? Try running the function for
different values of x and y.

```{r}
pow <- function(x, y) {
result <- x^y
print(paste(x,"raised to the power", y, "is", result))
}
```

**Solution**

A function to print x raised to the power y.

```{r eval=FALSE, include=FALSE}
pow(3,4)
```

-   [**Exercise 4.3**]{.underline}

onsider the earlier example of summing only the 2nd, 4th and 6th
elements of a defined vector x. Suppose we want to now define a function
for this calculation of adding up the elements in the even positions of
a vector x, where the length of x might vary. Write code to perform this
summation. Test your code using vector $x$ = (4,2,7,8,3,5,8,9,2,4,3,14).

Hint: The command length(x) will give you the number of elements in
vector x

**Solution**

```{r eval=FALSE, include=FALSE}
sum_even_x <- function(x)
{
sum_x <- 0
y<-length(x)/2
for (i in 1:y) sum_x<-sum_x+x[2*i]
print(sum_x)
}
x<-c(4,2,7,8,3,5,8,9,2,4,3,14)
sum_even_x(x)
```
