---
title: "Hypothesis Testing 1"
author: "Oscar Rodriguez de Rivera"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

In this worksheet we will explore different ways to carry out hypothesis testing in R. We will study examples of hypothesis testing for the mean $\mu$ and the variance $\sigma^2$ of a population which is assumed to be normal.

### Hypothesis testing based on a random sample from $N(\mu,\sigma^2)$

#### Hypothesis test for the mean $\mu$ when $\sigma^2$ is known

Suppose we have a random sample $X_1,X_2,...,X_n$ from the normal distribution $N(\mu,\sigma^2)$. We want to test the hypothesis

$$
\text{H}_{0}: \mu = \mu_0 \  versus \ \ \  \text{H}_1: \mu \neq \mu_0
$$

We know that under $\text{H}_{0}$,
$$
T = \frac{\bar{X}-\mu_0}{\sigma/\sqrt{n}} \sim \text{N}(0,1)
$$
and so we will reject $\text{H}_{0}$ at the $100\alpha\%$ level if $|T| > z_\frac{\alpha}{2}$

-   [**Exercise 1.1**]{.underline}

Suppose we are interested in the mean starting salary (in £’000s) for the students of the School of Maths, Stats and Act Sci of the University of Kent. We know from a previous study that the population follows a normal distribution N($\mu$,40) and a random sample of 35 graduates is taken: 

35, 23, 34, 56, 29, 25, 28, 45, 29, 34, 32, 31, 30, 35, 45, 27, 29, 40

39, 32, 29, 23, 24, 29, 29, 30, 28, 31, 25, 26, 28, 25, 26, 24, 21.

Two experts on labour economics claim the following:

* Economist 1: The mean starting salary is $\mu$ = 29.
* Economist 2: The mean starting salary is $\mu$ = 45.

Assess the claims of the two economists.

**Solution:** 

As discussed in the lecture (but here using a sample size of 35 rather than 40), if Economist 1 is correct, $\bar{X} ∼ N(29, \frac{40}{35})$ and so the test is

$$
\text{H}_{0}: \mu = 29 \ \ \  versus \ \ \  \text{H}_1: \mu \neq 29
$$

Enter the data into vector data1 and calculate the sample mean:

```{r}
data1<-c(35,23,34,56,29,25,28,45,29,34,32,31,30,35,45,27,29,40,39,32,29,23,24,29,29,
         30,28,31,25,26,28,25,26,24,21)
xbar<-mean(data1)
xbar
```

The sample mean is 30.74285

Now set the sample size, the mean assumed under the null hypothesis and the standard deviation:

```{r}
n<-length(data1)
m0_econ1 <- 29
sd <- sqrt(40)
```

Calculate the value of the test statistic and print it:

```{r}
z <- (xbar-m0_econ1)/(sd/sqrt(n))
z
```

The value of the test statistic is z = 1.630294

Find the critical values for the 5\% significance level:

```{r}
alpha <- .05
z.half.alpha <- qnorm(1-alpha/2)
c(-z.half.alpha, z.half.alpha)
```

The critical values for a 5% significance level are -1.959964 and 1.959964.
Should we reject the null hypothesis? Why/why not?

```{r eval=FALSE, include=FALSE}
#Since the value of the test statistic, 1.630294, is not in the tails of the disitrbution when compared with the critical values ± 1.959964, we cannot reject the null hypothesis at the 5% level.
```

What can you conclude from this hypothesis test?

```{r eval=FALSE, include=FALSE}
#There is no evidence against Economist 1’s claim, i.e. the mean starting salary could be 29.
```

Now carry out a similar hypothesis test to assess the claim of Economist 2.

if Economist 1 is correct, $\bar{X} ∼ N(45, 1)$ and so the test is

$$
\text{H}_{0}: \mu = 45 \ \ \  versus \ \ \  \text{H}_1: \mu \neq 45
$$

```{r}
m0_econ2 <- 45                        # true value under the null hypothesis
z2 <- (xbar-m0_econ2)/(sd/sqrt(n))    #realised value of the test statistic
z2
```

test at 5\% significance level
```{r}
alpha = .05
z.alpha.half = qnorm(1-alpha/2)
c(-z.alpha.half, z.alpha.half)
```

Since the value of the test statistic, -13.33634, is in the tails of the distribution when compared with the critical values $\pm 1.959964$, we reject the null hypothesis at the 5\% level. As the value of the test statistic is so far into the tails it would be sensible to consider smaller significance levels so you can reflect the full weight of evidence against the null hypothesis. Using the 5\% significance level we can conclude that there is some evidence that Economist 2’s claim is incorrect, i.e. the mean starting salary is not 45. Considering smaller significance levels will show that this evidence is very strong.

#### Hypothesis test for the mean when $\sigma^2$ is not known

If the variance is not known, we will have to use the t-distribution. The test statistic is now given by

$$
T=\frac{\bar{X}-\mu_{0}}{S/\sqrt{n}},
$$
where S is the square root of the sample variance $S^2$. We reject $\text{H}_0$ at the $100\alpha\%$ if $|T|>t_{n-1,\alpha/2}$

-   [**Exercise 1.2**]{.underline}

Suppose in Exercise 1.1 the variance is not known. Test the hypotheses at the 5\% significance level to assess the claims of the two economists.

**Solution:** Since the variance is not known we need to estimate it using the sample variance and then test the hypothesis using the t-distribution. From the following, note down the value of the sample standard deviation and the values of the test statistics for Economist 1’s and Economist 2’s claim

```{r}
sd<-sqrt(var(data1))
sd
t1 <- (xbar-m0_econ1)/(sd/sqrt(n)) #Economist’s 1 guess - t value
t1
mo_econ2<-45
t2 <- (xbar-m0_econ2)/(sd/sqrt(n)) #Economist’s 2 guess - t value
t2
```

sd = 7.20434, test statistic for Economist 1’s guess = 1.431204, test statistic for Economist 2’s guess = -11.70772

*Find the critical values $\pm t_{n−1,0.025}$ and note them down:*

```{r}
t.half.alpha <- qt(1-alpha/2, df=n-1) 
c(-t.half.alpha, t.half.alpha)
```

*How have your test statistics changed? How have your critical values changed? Do your conclusions change? Why/why not?*

The estimate of the standard deviation is slightly larger than the known value, which reduces the modulus of the test statistic. The critical values are more extreme than those from the standard normal distribution to allow for the estimation of the variance. The conclusion is still that Economist 1’s claim could be correct, but there is strong evidence that Economist 2’s claim is incorrect.

*Alternatively, we can use the built-in function of R, t.test:*

```{r}
t.test(data1,mu=29)
```

Use a similar command to test Economist 2’s claim.

```{r}
t.test(data1,mu=45)
```

Suppose now that for the data in Exercise 1.1 we want to test the following hypothesis:

$$
\text{H}_{0}: \mu = 29 \ \ \  versus \ \ \  \text{H}_1: \mu > 29
$$

Using the `t.test()` function we can do this in the following way: 
```{r}
t.test(data1,mu=29,alternative="greater")
```
Note the p-value. Would you reject the null hypothesis at the 10\% level? At the 5\% level?

$p$-value $<$ 0.1 $\rightarrow$ reject the null hypothesis at the 10\% level; $p$-value $>$ 0.05 $\rightarrow$ do not reject the null hypothesis at the 5\% level.

Note also the 95\% CI for mean income. How does this link with your conclusions above?

The 95\% CI is $[28.28372, \infty)$. The 95\% CI includes the hypothesised mean under the null hypothesis (29) so the null hypothesis is not rejected at the 5\% level.

#### Hypothesis test for the variance

Consider again a random sample $X_1, . . . , X_n$ from N($\mu, \sigma^2$) where we want to test the hypothesis

$$
\text{H}_{0}: \sigma^2 = \sigma^2_0 \ \ \  versus \ \ \  \text{H}_1: \sigma^2 \neq \sigma^2_0
$$
Under $\text{H}_0$

$$
T=\frac{(n-1)S^2}{\sigma^2_0} \sim \chi^2_{n-1}
$$
and so we reject $\text{H}_0$ at the $100(1-\alpha)\%$ level when $T < \chi^2_{n-1,1-\alpha/2}$ or $T > \chi^2_{n-1,\alpha/2}$.

-   [**Exercise 1.3**]{.underline}

Using the same data set as in Exercise 1.1, test whether the variance is 40

**Solution:**

1. Set df to n-1 (use length(data1)-1)
2. Set s2.0 to the value for $\sigma^2$ under the null hypothesis
3. Set alpha to correspond to a 5\% significance level
4. Find the lower critical value $(\chi^2_{n-1,1-\alpha/2}$ using qchisq(alpha/2, df) and the upper critical value $(\chi^2_{n-1,\alpha/2}$ using qchisq(1-alpha/2,df)
5. Set var1 to the sample variance of data1 (use var(data1))
6. Calculate the test statistic, t (you should get 44.11714)
7. Calculate the 95% confidence interval for the variance using

$$
\Bigg[\frac{(n-1)S^2}{\chi^2_{n-1,\alpha/2}},\frac{(n-1)S^2}{\chi^2_{n-1,1-\alpha/2}}\Bigg]
$$
What should you conclude? Do you have evidence that the variance is different from 40?

**Solution:**

```{r eval=FALSE, include=FALSE}
df <- length(data1)-1
s2.0<-40                       #variance under H_0
chi.upper<- qchisq(1-alpha/2, df)  #lower 1-alpha/2 percentile
chi.lower<- qchisq(alpha/2, df)
var1<-var(data1)
var1
```

```{r eval=FALSE, include=FALSE}
t<-df*var1/s2.0
#lower alpha/2 percentile
t
```

```{r eval=FALSE, include=FALSE}
CI<-c(df*var1/chi.upper,df*var1/chi.lower)
CI
```

```{r eval=FALSE, include=FALSE}
#The outcome of the hypothesis test at the 5% level can be determined either from the test statistic and critical values or from the 95% CI. As the 95% CI includes the value 40, a variance of 40 cannot be rejected at the 5% significance level. There is no evidence to suggest that the variance is different from 40.
```